Moral Foundations of U.S. Political News Organizations

### 2019-02-09 pilot_manuscript.Rmd
updated small tweaks
fixed citations and updated .bib file

# Method
For Experiment 1, the researchers approached the study with the intention to answer a method question. That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary. The researchers hypothesized the news sources genrally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*). Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.

@@

Concurrent research by Jordan, Buchanan, and Padfield is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples. The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation. The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD. Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).

@@

As in Experiment 1, the text was scanned with *ngram*. Again, blank articles, text from the Disqus system, and duplicate articles were removed [@Schmidt2017]. The text was processed and stemmed in order to convert to a usable form for further analysis [@Feinerer2017]. Words were subsequently matched with their valences from @Warriner2013. Depending on the results of Jordan, Buchanan & Padfield's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.

@@

# Experiment 2 results

@@

How it turned out

Limitations of this one (no rationale behind choosing sources except "people say NPR's liberal??")

What to do for future project (focus on one MF? Different sources? More sources?)

Argue: why is still a good thing to study?? (probably something about current state of discourse, information, truth, "alternative facts," subjective reality - philosophical stuff)

>>>>

For Experiment 1, the researchers approached the study with the intention to answer a method question. That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary. The researchers hypothesized the news sources genrally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*). Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.

@@

Concurrent research by @Jordan2019 is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples. The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation. The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD. Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).

@@

As in Experiment 1, the text was scanned with *ngram*. Again, blank articles, text from the Disqus system, and duplicate articles were removed [@Schmidt2017]. The text was processed and stemmed in order to convert to a usable form for further analysis [@Feinerer2017]. Words were subsequently matched with their valences from @Warriner2013. Depending on the results of @Jordan2019's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.

@@

## Results

@@
